---
title: "Compare Allison's fish-obs table to my fish-obs table"
output: html_notebook
---
This document was created to make sure that Michelle's fish-obs table is not missing any recapture events.

```{r setup, include=FALSE}
# load libraries
library(tidyverse)
library(here)
```

```{r}
# load data
agd <- readRDS("~/Downloads/marked_fish.RData")

mrs <- readRDS(here("data", "fish-obs.RData"))
```

Is there a fish table id in Allison's table that is not in Michelle's table
```{r}
(mrs_missing <- agd %>% 
  filter(!fish_table_id %in% mrs$fish_table_id))
```
Is there a fish table id in Michelle's table that is not in Allison's table
```{r}
(agd_missing <- mrs %>% 
   filter(!fish_table_id %in% agd$fish_table_id))
```
Do we have the same number of individuals
```{r}
agd_num <- agd %>% 
  group_by(fish_id) %>% 
  count()

mrs_num <- mrs %>% 
  group_by(fish_indiv) %>% 
  count()

(nrow(agd_num) == nrow(mrs_num))
```

Join tables by fish table id and see which rows are different between the 2 tables
```{r}
joined <- left_join(agd, select(mrs, fish_table_id, fish_indiv, gen_id, tag_id), by = c("fish_table_id", "gen_id", "tag_id"))

# change Allison's fish_id to be comparable to fish_indiv
(thing <- joined %>% 
  mutate(other = substr(fish_id, 4, 20)) %>% 
  filter(other != fish_indiv))
```
All of these fish are tag_recaptures that were assigned to multiple gen_ids.  In Michelle's table, the gen_id and fish_inidiv don't match because either cervus did not assign them as genetic recaptures or Michelle's script to re-assign gen_ids based on genetic recaptures missed them.  Michelle will invesitage and add notes to the fish-obs.RData table to document that the tag scanner has been checked and the identity analysis has been checked to verify that they are indeed tag recaptures but not genetic recaptures.