---
title: "Find individual fish in the database"
output: 
  github_document: default
  html_notebook: default
---
DO NOT RUN THIS SCRIPT WITHOUT RUNNING 05 AND 06 FIRST.  THIS SCRIPT IS NOT INTENDED TO RUN ON A PRE-EXISTING FISH-OBS FILE THAT CONTAINS A NOTES COLUMN AND A FISH_INDIV COLUMN.

This notebook finds fish that were tag recaptured and genetically recaptured and connects all of the observations of those fish, assigning them an individual id (fish_indiv) so all rows involving one fish can be found.

```{r setup, include=FALSE}
# knitr::opts_chunk$set(eval = FALSE)

# load libraries
library(tidyverse)
library(here)
# library(clownfishr)
# library(tidylog)
 
# load functions
source("~/db-connections.R")

# connect to database
leyte <- read_db("Leyte")
```

Find all fish that have been genetically or tag recaptured
```{r recaps}
# load the table of all fish with genids and tag ids
fish_obs <- read_csv("https://github.com/pinskylab/genomics/raw/master/data/fish-obs.csv", col_types = cols(
  fish_table_id = col_double(),
  sample_id = col_character(),
  tag_id = col_character(), # because numeric uses scientific notation and loses the end numbers
  gen_id = col_double()))

# assign a fish_indiv to each fish
fish_inds <- fish_obs %>% 
  # if a row has a gen_id but not a tag_id
  mutate(fish_indiv = ifelse(is.na(tag_id), gen_id, NA)) %>% 
  # if a row has a tag_id but not a gen_id
  mutate(fish_indiv = ifelse(is.na(gen_id), tag_id, fish_indiv)) %>% 
# for fish that have both a tag_id and gen_id, use gen_id
  mutate(fish_indiv = ifelse(!is.na(gen_id) & !is.na(tag_id), gen_id, fish_indiv))

# loop to make sure all recaptures of a fish get the same fish_indiv - takes about a minute
for_processing <- fish_inds
new_fish_indv <- tibble()

#this takes about 25 seconds
Sys.time()
while(nrow(for_processing) >= 1){
  # all rows that belong to this fish_table_id
  fti <- for_processing %>% 
    filter(!is.na(fish_table_id), 
      fish_table_id == for_processing$fish_table_id[1])
  
 # all rows that belong to the fish_indiv in the above table (and then join the above table)
  f_indiv <- for_processing %>% 
    filter(!is.na(fish_indiv), 
      fish_indiv == fti$fish_indiv) %>% 
    rbind(fti) %>% 
    distinct
  
  # all rows that contain these tag ids in the above table (and then join the above table)
  ti <- for_processing %>% 
    filter(!is.na(tag_id),
      tag_id %in% f_indiv$tag_id) %>% 
    rbind(f_indiv) %>% 
    distinct
  
  # all rows that contain these gen_ids in the above table (and then join the above table)
  gi <- for_processing %>% 
    filter(!is.na(gen_id), 
      gen_id %in% ti$gen_id) %>% 
    rbind(ti) %>% 
    distinct
  
  # what is the lowest indiv id in the table?
  min_indv <- min(gi$fish_indiv)
  
  # make all indv ids the same (the lowest)
  one_indiv <- gi %>% 
    mutate(fish_indiv = min_indv)
  
  # remove these rows from the for_processing table
  for_processing <- anti_join(for_processing, one_indiv, by = "fish_table_id")
  
  new_fish_indv <- rbind(new_fish_indv, one_indiv) %>% 
    distinct()

}

Sys.time()

# test - are there repeat fish_table_ids - should return 0 rows
test <- new_fish_indv %>% 
  group_by(fish_table_id) %>% 
  filter(n()> 1)
rm(test)

# add the fish_notes column from the database
fish_notes <- leyte %>% tbl("clownfish") %>% collect() %>% 
  filter(fish_table_id %in% new_fish_indv$fish_table_id) %>% 
  select(fish_table_id, fish_notes)

noted_fish_indv <- new_fish_indv %>% 
  left_join(fish_notes, by = "fish_table_id") %>% 
  rename(obs_notes = fish_notes)




saveRDS(noted_fish_indv, here::here("data", "fish-obs.rds"))
saveRDS(noted_fish_indv, here("data", "fish-obs.RData"))

# save Rdata files as csv for easy reading from github
# new_fish_indv <- readRDS(save_loc)
write_csv(noted_fish_indv, here("data", "fish-obs.csv"))

noted_fish_indv
```


