---
title: "Plot of size of clownfish when change from Male to Female"
output: 
  github_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
#This line of code installs the pacman page if you do not have it installed - if you do, it simply loads the package
# if(!require(pacman))install.packages("pacman")

# change install to true if you want to install any packages listed that you don't currently have.
# pacman::p_load(here, clownfish, dplyr, ggplot2, install = FALSE)
# library(here)
# library(clownfish)
# library(dplyr)
# library(ggplot2)


# db connection still not working
source("../../clownfish-pkg/R/db_connections.R")
source("../../clownfish-pkg/R/funs-sample-meta.R")
leyte <- read_db("Leyte")
```

```{r load data, include=FALSE}
recaps <- readRDS(here("data", "recaptured-fish.Rdata"))
```

Which recaptured fish changed sex?
```{r sex change, include=FALSE}
recap_fish <- fish_anem_dive() %>% 
  filter(fish_table_id %in% recaps$fish_table_id)  %>% 
  rename(dive_date = date)%>% 
  select(fish_table_id, sex, size, dive_date) %>% 
  right_join(recaps, by = "fish_table_id")

sex_change <- recap_fish %>% 
  select(recap_id, sex) %>% 
  filter(!is.na(sex)) %>% 
  distinct() %>% 
  group_by(recap_id) %>% 
  count() %>% 
  filter(n > 1)

recap_fish_change <- recap_fish %>%
  filter(recap_id %in% sex_change$recap_id) %>%
  arrange(recap_id, dive_date) %>% 
  select(recap_id, dive_date, sex, size)
```


Which sex changes involve becoming Female?
*note all of these changes are not male to female, some are juvenile to female*
```{r to female, include=FALSE}
# which sex changes involve becoming Female?
# note all of these changes are not male to female, some are juvenile to female
females <- recap_fish_change %>% 
  filter(sex == "F")

# remove multiple observations of the same fish
dups <- females %>% 
  group_by(recap_id) %>% 
  count() %>% 
  filter(n > 1)

for (i in seq(dups$recap_id)){
  x <- females %>% 
    filter(recap_id == dups$recap_id[i]) %>% 
    arrange(dive_date)
  
  if(nrow(x) > 1){
    x <- x %>% 
      slice(2:nrow(x))
    females <- anti_join(females, x, by = c("recap_id", "dive_date", "sex", "size"))
  }
}
```
To find out which fish went from J to F vs. which fish went from M to F, dive deeper
```{r}
# find sex changes that involve becoming F
to_F <- recap_fish_change %>% 
  filter(recap_id %in% females$recap_id)

# find sex changes that involve M
with_M <-  to_F %>% 
  filter(sex == "M")

M_to_F <- to_F %>% 
  filter(recap_id %in% with_M$recap_id) %>% 
  rename(date = dive_date)

females_from_males <- females %>% 
  filter(recap_id %in% M_to_F$recap_id)

females_from_juveniles <- females %>% 
  filter(!recap_id %in% M_to_F$recap_id)

saveRDS(females_from_males, here("data", "females_from_males.RData"))
saveRDS(females_from_juveniles, here("data", "females_from_juveniles.RData"))
```
M_to_F made some sex assignments very clearly incorrect.  Going to fix the db in leyteBuildDB and then come back and re-run code to this point and re-examine M_to_F table, in order to do this, need fish_table_ids
```{r, eval=FALSE, include=FALSE}
with_fti <- left_join(M_to_F, recaps, by = c("recap_id","date")) %>% 
  select(fish_table_id, recap_id, sex, size, date) %>% 
  arrange(recap_id, date)
```





Which sex changes involve becoming Male?
```{r j to M, include=FALSE}
males <- recap_fish_change %>% 
  filter(sex == "M")

juveniles <- recap_fish_change %>% 
  filter(sex == "J")

# remove sex changes that do not involve a juvenile (remove male to female only sex changes) because we want to know the size to go from juvenile to male, not male to female.

males <- males %>% 
  filter(recap_id %in% juveniles$recap_id)

# remove multiple observations of the same fish
dups <- males %>% 
  group_by(recap_id) %>% 
  count() %>% 
  filter(n > 1)

for (i in seq(dups$recap_id)){
  x <- males %>% 
    filter(recap_id == dups$recap_id[i]) %>% 
    arrange(dive_date)
  
  if(nrow(x) > 1){
    x <- x %>% 
      slice(2:nrow(x))
    males <- anti_join(males, x, by = c("recap_id", "dive_date", "sex", "size"))
  }
}
```


```{r plot females, message=FALSE, echo=FALSE}
	c <- ggplot(females, aes(as.numeric(size)
	                         # , binwidth = 1
	                         ))
	
	c + geom_density(kernel = "gaussian") + 
	  theme_classic()+
	  labs(title = "Distribution of sizes at sex change to female", 
	       subtitle = "from either juvenile or male", 
	       x = "Size at first F observation", 
	       y = "count") 
	
	ggsave(filename = here("plots", "female-distribution-size-color-change.pdf"))
	saveRDS(females, here("data", "recap_first_female.RData"))
```

```{r plot males, message=FALSE, echo=FALSE}	
		c <- ggplot(males, aes(as.numeric(size)))
	
	c + geom_density(kernel = "gaussian") + 
	  theme_classic()+
	  labs(title = "Distribution of sizes at sex change to male", 
	       subtitle = "from juvenile", 
	       x = "Size at first M observation", 
	       y = "count") 
	
	ggsave(filename = here("plots", "female-distribution-size-color-change.pdf"))
	saveRDS(males, here("data", "recap_first_male.RData"))
```

