---
title: "Which tag recaptured fish have been genotyped"
output: html_notebook
---



```{r setup, include = FALSE}
library(tidyverse)
library(clownfish)
library(here)

# while db connection using helper file isn't working 
source("~/Documents/clownfish-pkg/R/db_connections.R")
leyte <- read_db("Leyte")
lab <- read_db("Laboratory")
```
Fish that are tag recaptures who also have been geneotyped more than once
```{r}
fish <- fish_anem_dive() %>% 
  select(fish_table_id, sample_id, tag_id, recap, gen_id, anem_table_id, fish_obs_time, anem_obs_time, date, anem_id, anem_obs, gps) 

# multiple observations of the same tag_id
tag_recap <- fish %>% 
  # only tagged fish that have been genotyped
  filter(!is.na(gen_id) & !is.na(tag_id)) %>% 
  group_by(tag_id) %>% 
  count() %>% 
  filter(n > 1) %>% 
  ungroup() 

tag_gen <- fish %>% 
  filter(tag_id %in% tag_recap$tag_id, 
         !is.na(gen_id)) %>% 
  arrange(tag_id)


# add ligation ids
lig_tag_gen <- lig_from_samp(tag_gen$sample_id) %>% 
  right_join(tag_gen, by = "sample_id") %>% 
  filter(!is.na(ligation_id))

lig_tag_gen %>% 
  select(ligation_id, sample_id, tag_id, gen_id)
```

Genotyping matchups for these fish
```{r}
all_ids <- read_csv(here("data", "seq03-33_identity", "33-03_seq_identity_ID_all.csv")) %>% 
  janitor::clean_names() %>% 
  filter(first_id %in% lig_tag_gen$ligation_id | second_id %in% lig_tag_gen$ligation_id) %>% 
  select(-p_id, -p_i_dsib, -status) %>% 
  mutate(mismatch_prop = mismatching_loci/(mismatching_loci + matching_loci))

fish_pairs <- tibble()
process <- lig_tag_gen
while(nrow(process >= 1)){
  # which fish are tag matches?
  x <- process %>% 
    filter(tag_id == process$tag_id[1]) %>% 
    select(ligation_id, sample_id, gen_id, tag_id)
  
  y <- all_ids %>% 
    filter(first_id == x$ligation_id[1] & second_id == x$ligation_id[2])
  if(nrow(y) == 0){
    y <- all_ids %>% 
    filter(first_id == x$ligation_id[2] & second_id == x$ligation_id[1])
  }
  
  z <- y %>% 
    left_join(x, by = c("first_id" = "ligation_id")) %>% 
    rename(first_sample_id = sample_id, 
           first_tag_id = tag_id, 
           first_gen_id = gen_id, 
           first_loci_typed = loci_typed) %>% 
    left_join(x, by = c("second_id" = "ligation_id")) %>% 
      rename(second_sample_id = sample_id, 
           second_tag_id = tag_id, 
           second_gen_id = gen_id, 
           second_loci_typed = loci_typed_1) %>% 
    select(contains("match"),contains("first"), contains("second"), everything())
    
  fish_pairs <- rbind(fish_pairs, z)
  # remove those rows from samples to still be processed
  process <- process %>% 
    filter(!gen_id %in% x$gen_id)
  
  
  
}

fish_pairs %>% select(mismatch_prop, first_gen_id, second_gen_id, everything())

write_csv(fish_pairs, here("data", "genotyped-tag-recaps.csv"))
```

L3037 does not appear to be in the identity analysis.  It was removed because there is a potential lab error with the sample so it is in the known issues table.

Tag_id 985153000375244 is in 2 fish that have 25% mismatch proportion.  Check the scanner.  The observations of these fish are correct but I question the integrity of the lab sample.
```{r}
pitscan <- leyte %>% 
  tbl("pitscan") %>% 
  collect() %>% 
  filter(tag == 153000375244)

fish <- fish_anem_dive() %>% 
  filter(tag_id == 985153000375244)

fish
```


