---
title: "2019-09-16 dDocent re-run"
output: html_notebook
---

```{r setup}
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(purrr)
```

Ran dDocent, entered manually on the command line, started on 9/16/2019

- Checked in on the run at 10:30am on Tuesday, 9/17/2019 and it was running samtools on L0355.  Still a long ways to go.
- Checked at 6:45am on Wednesday, 9/18/2019, running bedtools and writing to mapped.bed
- Checked at 2pm on 9/19/2019, running freebayes
- Checked at 8:55am on 9/20/2019, running freebayes
- checked at 11:00am on 9/21/2019, running freebayes, 26gig of memory free in the buffers/cache

Finished on Sunday, 9/22/2019.

Did it include the files from known_issues?

```{bash eval=FALSE}
cp /data/apcl/all_samples/20190916/namelist ./
```


```{r}

samples <- tibble(ligation_id = read_lines("namelist")) %>% 
  mutate(ligation_id = str_replace(ligation_id, "APCL_", ""))

issues <- readRDS(here::here("data", "known_issues.rds"))
write_csv(issues, here::here("data", "known_issues.csv"))

missing <- anti_join(issues, samples, by = "ligation_id") %>% 
  filter(!grepl("do not use", issue),
         !grepl("Non-APCL", issue))

not_missing <- map_dfr(unique(missing$ligation_id), ~samples %>% filter(grepl(.x, ligation_id))) %>% 
  separate(ligation_id, into = c("ligation_id", "regeno"), sep = "\\.")

found <- not_missing %>% 
  select(regeno) %>% 
  rename(ligation_id = regeno) %>% 
  rbind(select(not_missing, ligation_id)) %>% 
  filter(ligation_id != "F")

missing <- anti_join(missing, found, by = "ligation_id") %>% 
  arrange(ligation_id)

write_csv(missing, here::here("data", "missing_from_all_samples.csv"))
```

```{bash}
mkdir /data/apcl/all_samples/20190925

mv /local/home/michelles/02-apcl-ddocent/regenos/L1607_L1042.F.fq.gz /data/apcl/all_samples/20190925/L1607.L1042.F.fq.gz

mv /local/home/michelles/02-apcl-ddocent/regenos/L0936_L3145.F.fq.gz /data/apcl/all_samples/20190925/L0936.L3145.F.fq.gz

mv /local/home/michelles/02-apcl-ddocent/regenos/L0973_L3122.F.fq.gz /data/apcl/all_samples/20190925/L0973.L3122.F.fq.gz

mv /local/home/michelles/02-apcl-ddocent/regenos/L0697_L3021.F.fq.gz /data/apcl/all_samples/20190925/L0697.L3021.F.fq.gz

mv /local/home/michelles/02-apcl-ddocent/regenos/L2716_L3169.F.fq.gz /data/apcl/all_samples/20190925/L2716.L3169.F.fq.gz





```

