---
title: "Analysis of clownfish movement"
output: html_notebook
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, here, clownfish, geosphere, sf, maps, ggthemes, leaflet, install=FALSE)
# library(tidylog)
source("~/Documents/clownfish-pkg/R/db_connections.R")
leyte <- read_db("Leyte")
```

Find all fish that have been recaptured
```{r recaps}
fish <- fish_anem_dive() %>% 
  select(fish_table_id, sample_id, tag_id, recap, gen_id, anem_table_id, fish_obs_time, anem_obs_time, date, anem_id, anem_obs, gps) 

# multiple observations of the same tag_id
tag_recap <- fish %>% 
  group_by(tag_id) %>% 
  count() %>% 
  filter(n > 1 & !is.na(tag_id)) %>% 
  ungroup() %>%
  mutate(tag_recap_id = 1:nrow(.))

# multiple observations of the same genetically identified fish
gen_recap <- fish %>% 
  group_by(gen_id) %>% 
  count() %>% 
  filter(n > 1 & !is.na(gen_id)) %>% 
  ungroup() %>% 
  mutate(gen_recap_id = 1:nrow(.))

# join these back to fish for complete info
fish_recaps <- fish %>% 
  filter(gen_id %in% gen_recap$gen_id | tag_id %in% tag_recap$tag_id)



# need to create a recap_id to match these fish up
fish_recaps <- left_join(fish_recaps, select(tag_recap, -n), by = "tag_id")
fish_recaps <- left_join(fish_recaps, select(gen_recap, -n), by = "gen_id")

# add 300 to gen_recap_id to make sure it is not duplicated in tag_recap_id
fish_recaps <- fish_recaps %>% 
  mutate(gen_recap_id = gen_recap_id + 300) %>%
  # if tag_recap_id is NA and gen_recap_id isn't
  mutate(recap_id = ifelse(is.na(tag_recap_id), gen_recap_id, NA)) %>% 
  # if tag_recap_id isn't and gen_recap_id is NA
  mutate(recap_id = ifelse(is.na(gen_recap_id), tag_recap_id, recap_id))

# if there is a value in both columns, need to get all of them
multi_caps <- fish_recaps %>% 
  filter(is.na(recap_id)) %>% 
  select(tag_id, tag_recap_id, gen_id, gen_recap_id, recap_id) %>% 
  distinct()

results <- tibble()

for (i in seq(nrow(multi_caps))){
  x <- fish_recaps %>% 
    filter(gen_id == multi_caps$gen_id[i] | tag_id == multi_caps$tag_id[i]) %>% 
    arrange(recap_id) %>% 
    mutate(new_recap_id = recap_id[1])
  
  if (is.na(x$new_recap_id[1])){
  x <- x %>% 
    mutate(new_recap_id = gen_recap_id[1])
  }
  
  stopifnot(!is.na(x$new_recap_id))
  
  
  results <- rbind(results, x)
}

results <- results %>% 
  select(fish_table_id, new_recap_id)

fish_recaps <- left_join(fish_recaps, results, by = "fish_table_id")

fish_recaps <- fish_recaps %>% 
  mutate(recap_id = ifelse(!is.na(new_recap_id), new_recap_id, recap_id))


# add lat longs
fish_coords <- fish_recaps %>% 
 mutate(anem_obs_time = lubridate::force_tz(lubridate::ymd_hms(str_c(date, anem_obs_time, sep = " ")), tzone = "Asia/Manila"),
           # convert to UTC
           anem_obs_time = lubridate::with_tz(anem_obs_time, tzone = "UTC"),
           gpx_date = lubridate::date(anem_obs_time),
           gpx_hour = lubridate::hour(anem_obs_time),
           minute = lubridate::minute(anem_obs_time))

  gpx <- leyte %>%
    tbl("GPX") %>%
    select(lat, lon, time, unit) %>%
    collect() %>%
    separate(time, into = c("gpx_date", "gps_time"), sep = " ") %>%
    mutate(gpx_date = lubridate::date(gpx_date)) %>%
    filter(gpx_date %in% fish_coords$gpx_date) %>%
    separate(gps_time, into = c("gpx_hour", "minute", "second"), sep = ":") %>%
    filter(as.numeric(gpx_hour) %in% fish_coords$gpx_hour & as.numeric(minute) %in% fish_coords$minute) %>%
    mutate(gpx_hour = as.numeric(gpx_hour),
           minute = as.numeric(minute))
  
  # find matches for times to assign lat long - there are more than one set of seconds (sec.y) that match
  temporary <- left_join(fish_coords, gpx, by = c("gps" = "unit",  "gpx_date","gpx_hour", "minute")) %>%
    mutate(lat = as.numeric(lat),
           lon = as.numeric(lon)) # need to make decimal 5 digits - why? because that is all the gps can hold

    
  # calculate a mean lat lon for each fish_coords observation
  coord <- temporary %>%
    group_by(fish_table_id) %>% 
    summarise(lat = mean(lat, na.rm = TRUE),
              lon = mean(lon, na.rm = T))

  fish_locs <- left_join(fish_coords, coord,  by = "fish_table_id") %>% 
    select(fish_table_id, gen_id, tag_id, lat, lon, recap_id) %>% 
    # remove fish for which there are no coordinates (one fish for which it appears Malin's gps was turned off during capture)
    filter(!is.na(lat))
# decided not to create a loc column
    # %>% 
  #   mutate(loc = paste(lon, lat, sep = ","))
  rm(fish_recaps)
 
```

This attempt to use geoDist isn't great because we almost need the p1 and p2 locaitons to be in the same row of the data frame.  Trying to create a polygon instead (see below this chunk).
```{r eval=FALSE} 
  # calculate the distance between capture points
  gen_caps <- distinct(fish_locs, gen_id) %>% 
    filter(!is.na(gen_id))
  # for every unique gen_id
for (i in seq_along(gen_caps$gen_id)){
  x <- fish_locs %>% 
    filter(gen_id == gen_caps$gen_id[i])
  # for every row that contains that specific gen_id
  for (j in seq_along(x$loc)){
    while(j < nrow(x))
      dist <- distGeo(p1 = c(x$lon[j], x$lat[j]), p2 = c(x$lon[j+1], x$lat[j+1]))
    
  }
}
  

```

Create a polygon to calcuate area of home range based on this stack overflow post
https://stackoverflow.com/questions/48383990/convert-sequence-of-longitude-and-latitude-to-polygon-via-sf-in-r
```{r home_range}
recaps <- unique(fish_locs$recap_id)
results <- tibble()

for (i in seq_along(recaps)){
  x <- filter(fish_locs, recap_id == recaps[i])
  
  # create a table of locations
  df <- data.frame(lon = c(x$lon), 
                   lat = c(x$lat))
  
  # close the polygon by adding the first line again
  df <- rbind(df, df[1, ])
  
  poly <- st_sf(st_sfc(st_polygon(list(as.matrix(df)))), crs = 4326)


  y <- tibble(recap_id = x$recap_id[1], home_range = st_area(poly))
  
  results <- rbind(results, y)
  
}

fish_locs <- left_join(fish_locs, results, by = "recap_id")

attr(fish_locs$home_range, "units")<- NULL

fish_locs$home_range <- as(fish_locs$home_range, "numeric")
```

Plot the distribution of home ranges
```{r area}
a <- ggplot(fish_locs, mapping = aes(home_range))

a + geom_area(stat = "bin")
```

```{r plot}
a <- ggplot(fish_locs, mapping = aes(home_range))

a + geom_histogram(binwidth = 1000)+
  xlim(0,30000)+
  ylim(0, 10)
```
Which fish have a greater home range than 100m?
```{r}
movers <- fish_locs %>% 
  distinct(recap_id, home_range) %>% 
  filter(home_range > 100)
```

Let's take a look at extremes
```{r}
farthest <- fish_locs %>% 
  filter(recap_id == 145)

farthest_meta <- fish_anem_dive() %>% 
  filter(fish_table_id %in% farthest$fish_table_id) %>% 
  select(site, anem_id, anem_obs, fish_obs_time, anem_obs_time, date, fish_table_id, sample_id, gen_id, tag_id, recap, fish_notes, anem_notes, dive_notes)

```
The fish that moved the farthest moved from Palanas to Wangag.  This seems feasible but we should double check the pit tags.
```{r}
pitscan <- leyte %>% 
  tbl("pitscan") %>% 
  collect() %>% 
  filter(date %in% farthest_meta$date) %>% 
  arrange(date, time) %>% 
  mutate(tag_id = paste0(city, tag))
```
One fish of interest tag_id is                    985153000401241

The fish captured on 2015-06-02 at 09:57 tag_id is 985153000401241 in Wangag, this tag_id is based on a pre-dive scan and what was written on the data sheet.
The fish captured on 2017-05-29 at 12:18 tag_id is 985153000401241 in Wangag
The fish captured on 2018-03-07 at 10:53 tag_id is 985153000401241 in Palanas.  This fish moved.
```{r}
mover_2 <- fish_locs %>% 
  filter(recap_id == 157)

mover_2 <- fish_anem_dive() %>% 
  filter(fish_table_id %in% mover_2$fish_table_id) %>% 
  select(site, anem_id, anem_obs, fish_obs_time, anem_obs_time, date, fish_table_id, sample_id, gen_id, tag_id, recap, fish_notes, anem_notes, dive_notes)

pitscan <- leyte %>% 
  tbl("pitscan") %>% 
  collect() %>% 
  filter(date %in% mover_2$date) %>% 
  arrange(date, time) %>% 
  mutate(tag_id = paste0(city, tag))
```
This fish is a genetic recapture that moved from Wangag to Palanas.

```{r}
mover_3 <- fish_locs %>% 
  filter(recap_id == 181)

mover_3 <- fish_anem_dive() %>% 
  filter(fish_table_id %in% mover_3$fish_table_id) %>% 
  select(site, anem_id, anem_obs, size, color, fish_obs_time, anem_obs_time, date, fish_table_id, sample_id, gen_id, tag_id, recap, fish_notes, anem_notes, dive_notes)

pitscan <- leyte %>% 
  tbl("pitscan") %>% 
  collect() %>% 
  filter(date %in% mover_3$date) %>% 
  arrange(date, time) %>% 
  mutate(tag_id = paste0(city, tag))
```
This fish was always captured at Visca but has a home range of 1500 meters and was never captured on the same anemone twice.




The fish that moved the farthest was seen in Palanas one day and Poroc San Flower the next.  This seems very unlikely.  
Let's double check pit scans
```{r eval=FALSE}
pitscan <- leyte %>% 
  tbl("pitscan") %>% 
  collect() %>% 
  # filter(date %in% farthest_meta$date) %>% 
  arrange(date, time) %>% 
  mutate(tag_id = paste0(city, tag))
```
One fish of interest tag_id is                    982000411818470

The fish captured on 2017-05-15 at 14:39 tag_id is 982000411818470 in Palanas
The fish captured on 2017-06-11 at 14:21 tag_id is 982000411818470 in Palanas
The fish captured on 2017-06-12 at 08:45 tag_id is 982000411818478 in Poroc San Flower - not the same fish.  Correcting database.

Can we map the location of movers? This is a bad map, don't run this chunk
```{r map, eval=FALSE}
leyte_map <- subset(map_data("world"), subregion == "Leyte")


map <- ggplot(data = leyte_map) +
  geom_polygon(aes(x = long, y = lat, group = group), fill = "gray80", colour = "gray85") +
  coord_fixed(1.3)

fish_map <- map + 
  geom_point(data = fish_locs, aes(lon, lat, color = recap_id)
             , alpha = 0.1
             , show.legend = FALSE)+
  theme_map()+
  labs(title = "Clownfish capture locations") 

fish_map
```

Try leaflet ot make a map.  This map also kind of sucks.  Can't get close enough or color the icons by recap_id.
```{r bad leaflet, eval=FALSE}
fishicon <- makeIcon(
  iconUrl = "https://www.flaticon.com/premium-icon/icons/svg/166/166713.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

greenLeafIcon <- makeIcon(
  iconUrl = "http://leafletjs.com/examples/custom-icons/leaf-green.png",
  iconWidth = 38, iconHeight = 95,
  iconAnchorX = 22, iconAnchorY = 94,
  shadowUrl = "http://leafletjs.com/examples/custom-icons/leaf-shadow.png",
  shadowWidth = 50, shadowHeight = 64,
  shadowAnchorX = 4, shadowAnchorY = 62
)

fish_locs %>% 
 leaflet() %>% 
  # add content
   addTiles() %>%
  # addProviderTiles(providers$Esri.WorldImagery) %>%
   addMarkers(clusterOptions = markerClusterOptions(), 
              popup = as.character(fish_locs$recap_id), 
              lat = fish_locs$lat, 
              lng = fish_locs$lon)
```



