---
title: "Identity Protocol for APCL project"
output: 
  html_notebook:
    code_folding: hide
    df_print: paged
    highlight: kate
---
# Workspace setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
pacman::p_load(tidyverse, lubridate, here, RMySQL, clownfish, janitor, geosphere, install=TRUE)
 # library(tidyverse)
 # library(lubridate)

# while db connection using helper file isn't working 
source("~/Documents/clownfish-pkg/R/db_connections.R")
leyte <- read_db("Leyte")
lab <- read_db("Laboratory")
```

This notebook continues where filtering and removing regenos left off, moving the genepop into cervus and processing identity results.
 
## Import the genepop to cervus
The no regenos genepop should be stored on github and downloaded onto the windows machine.  
- On the github website, click on the genepop (noregeno.gen).  
- Right click on "view raw" and save link as...  

###Open Cervus and convert the genepop to ceruvs:
 - Tools > Convert genotype file > Genepop to Cervus
 - A window will open, navigate to the genepop file that has been downloaded to the windows machine
 - Choose 2 digit format, do not use the first id as a population name
 **(2790 individuals, 1005 loci)**
 
### Run an allele frequency analysis:
 - Analysis > Allele frequency analysis
 - make sure the converted file is in the genotype file field
 * Yes Header Row
 * Yes Read Locus Names
 * ID in column 2
 * First allele in column 3
 * Type in number of loci from conversion (1005)
 * Save as “….._AF"
 * Leave all the output option boxes checked
  
### Run an identity analysis
 * Genotype file should be autofilled with the convert file created above
 * Yes Header Row
 * Id in column 2
 * First allele in column 3
 * Do not test sexes separately
 * Allele freq data should be autofilled with the AF file created above
 * Save as “…._ID"
 * Fill in minimum number of matching loci, this should be comparable to the amount of missing data allowed in the filtering step.  For example, if we allow 30% missing data for individuals during filtering, we should not require more than 70% matching loci.  Because the 70-30 line is the cutoff, 65% or 60% would include fish who are on the borderline. For this analysis 50% ()
 * allow fuzzy matching with 10% mismatch (10% of total = 145)
 * don’t show all comparisons - this generates a HUGE csv of every single pairwise comparison.
 
### Upload the output to github, pull to mac
 
### Import the data into R
 
```{r message=FALSE}
idcsv_raw <- read_csv(here::here("data", "seq03-33_identity", "33-03_seq_identity_ID.csv"), col_types = cols(
  `First ID` = col_character(),
  `Loci typed` = col_integer(),
  `Second ID` = col_character(),
  `Loci typed_1` = col_integer(),
  `Matching loci` = col_integer(),
  `Mismatching loci` = col_integer(),
  pID = col_double(),
  pIDsib = col_double(),
  Status = col_character()
)) 

names(idcsv_raw) <- c("first_id",  "first_loci_typed",  "second_id",  "second_loci_typed",  "matching_loci",  "mismatching_loci",  "p_id",  "p_id_sib",  "status")

# add mismatch rate
idcsv <- idcsv_raw %>%
  mutate(mismatch_prop = mismatching_loci/(mismatching_loci + matching_loci)) %>% 
  # order by number of matching loci
  arrange(matching_loci)
```


Plot proportion mismatch, pay attention to axis limits
```{r eval=FALSE}

ggplot(idcsv, aes(x = mismatch_prop, y = matching_loci)) +
  geom_point() +
  theme_bw()
 
```
#### Make a histogram of mismatch proportion
```{r}
idcsv %>% 
  ggplot(aes(mismatch_prop)) +
  geom_histogram(binwidth = 0.001)
```

### Add sample_ids
```{r}
 # for first_sample_id
 temp <- idcsv %>% 
   rename(ligation_id = first_id)
 lab1 <- samp_from_lig(temp)
 names(lab1) <- paste("first_", names(lab1), sep = "")
 
 
 # for second_sample_id
 temp <- idcsv %>% 
   rename(ligation_id = second_id)
 lab2 <- samp_from_lig(temp)
 names(lab2) <- paste("second_", names(lab2), sep = "")
 
 # add the ids to the idcsv
  idcsv <- idcsv %>% 
    left_join(lab1, by = c("first_id" = "first_ligation_id")) %>% 
    left_join(lab2, by = c("second_id" = "second_ligation_id")) 

rm(lab1, lab2, temp)
```
### Add gen_ids
```{r}
gen_ids <- readRDS(here::here("data", "fish-obs.RData")) %>% 
  select(sample_id, gen_id)

idcsv <- idcsv %>% 
  left_join(gen_ids, by = c("first_sample_id" = "sample_id")) %>% 
  rename(first_gen_id = gen_id) %>% 
  left_join(gen_ids, by = c("second_sample_id" = "sample_id")) %>% 
  rename(second_gen_id = gen_id)

```

### Add field data
```{r}
first <- fish_anem_dive() %>% 
  filter(sample_id %in% idcsv$first_sample_id)
names(first) <- paste0("first_", names(first))

sec <- fish_anem_dive() %>% 
  filter(sample_id %in% idcsv$second_sample_id)
names(sec) <- paste0("second_", names(sec))

idcsv <- left_join(idcsv, first, by = "first_sample_id") %>% 
  left_join(sec, by = "second_sample_id")

# rearrange columns
idcsv <- idcsv %>% 
  select(contains("first"), contains("second"), everything())

rm(first, sec)
```

## Get lat lons
```{r}

#find the lat lon of the first anem
first <- idcsv %>% 
  mutate(first_anem_obs_time = force_tz(ymd_hms(str_c(first_date, first_anem_obs_time, sep = " ")), tzone = "Asia/Manila")) %>% 
  mutate(first_anem_obs_time = with_tz(first_anem_obs_time, tzone = "UTC")) %>% 
  mutate(first_hour = hour(first_anem_obs_time), 
         first_minute = minute(first_anem_obs_time))

lat <- leyte %>%
    tbl("GPX")  %>% 
    mutate(gpx_date = date(time)) %>%
    filter(gpx_date %in% idcsv$first_date) %>% 
    mutate(gpx_hour = hour(time)) %>%
    mutate(minute = minute(time)) %>%
    mutate(second = second(time)) %>%
    select(-time, -second)%>%
    collect() 

# attach the lat lons
first <- left_join(first, lat, by = c("first_date" = "gpx_date", "first_hour" = "gpx_hour", "first_minute" = "minute", "first_gps" = "unit"))

# summarize the lat lons
first <- first %>% 
  group_by(first_id) %>% 
  summarise(first_lat = mean(as.numeric(lat)), 
            first_lon = mean(as.numeric(lon)))

idcsv <- left_join(idcsv, first, by = "first_id")
rm(first, lat)

# find the lat lon of the second anem
second <- idcsv %>% 
  mutate(second_anem_obs_time = force_tz(ymd_hms(str_c(second_date, second_anem_obs_time, sep = " ")), tzone = "Asia/Manila")) %>% 
  mutate(second_anem_obs_time = with_tz(second_anem_obs_time, tzone = "UTC")) %>% 
  mutate(second_hour = hour(second_anem_obs_time), 
         second_minute = minute(second_anem_obs_time))

lat <- leyte %>%
    tbl("GPX")  %>% 
    mutate(gpx_date = date(time)) %>%
    filter(gpx_date %in% idcsv$second_date) %>% 
    mutate(gpx_hour = hour(time)) %>%
    mutate(minute = minute(time)) %>%
    mutate(second = second(time)) %>%
    select(-time, -second)%>%
    collect() 

# attach the lat lons
second <- left_join(second, lat, by = c("second_date" = "gpx_date", "second_hour" = "gpx_hour", "second_minute" = "minute", "second_gps" = "unit"))

# summarize the lat lons
second <- second %>% 
  group_by(second_id) %>% 
  summarise(second_lat = mean(as.numeric(lat)), 
            second_lon = mean(as.numeric(lon)))

idcsv <- left_join(idcsv, second, by = "second_id")
rm(lat, second)  

```

# Write big table into a file 
```{r}
# saveRDS(idcsv, here::here("data", "identity_big-table.RData"))

# idcsv <- readRDS(here::here("data", "identity_big-table.RData"))
```

# Does the first gen_id match the second gen id?
```{r}
old_pairs <- idcsv %>% 
  filter(first_gen_id == second_gen_id, 
         !is.na(first_gen_id)) %>% 
  select(first_sample_id, second_sample_id, first_gen_id, second_gen_id, first_tag_id, second_tag_id, mismatching_loci, matching_loci, contains("lat"), contains("lon"), contains("sex"))
```


# Examine new matches
```{r message=FALSE}
new_pairs <- idcsv %>% 
  filter(first_gen_id != second_gen_id) %>% 
  # reduce number of columns
  select(first_sample_id, second_sample_id, first_gen_id, second_gen_id, first_tag_id, second_tag_id, mismatch_prop,mismatching_loci, matching_loci, contains("lat"), contains("lon"), contains("sex"), contains("date"), contains("site"), first_id, second_id, contains("notes"))

# make sure no known_issues are included
iss <- lab %>% 
  tbl("known_issues") %>% 
  collect()

new_pairs <- new_pairs %>% 
  filter(!first_id %in% iss$ligation_id, 
         !second_id %in% iss$ligation_id)


new_pairs$dist <- distGeo(new_pairs[, c("first_lon", "first_lat")], new_pairs[, c("second_lon", "second_lat")])

(new_pairs %>% select(first_sample_id, second_sample_id, dist, first_date, second_date, first_site, second_site, everything(), -contains("corr"), -contains("lat"), -contains("lon")))

```

# Which pairs are on the same ligation plate?
```{r}
# what plates were the new pairs on?
first <- new_pairs %>% 
  rename(sample_id = first_sample_id)
first <- work_history(first, "sample_id") %>% 
  filter(!is.na(lig_well))

names(first) <- paste("first", names(first), sep = "_")

new_pairs_first <- left_join(new_pairs, first, by = "first_sample_id")

second <- new_pairs_first %>% 
  rename(sample_id = second_sample_id)

second <- work_history(second, "sample_id") %>% 
  filter(!is.na(lig_well))

names(second) <- paste("second", names(second), sep = "_")

new_pairs <- left_join(new_pairs_first, second, by = "second_sample_id")



same_lig_plate <- new_pairs %>% 
  filter(first_lig_plate == second_lig_plate) %>% 
  select(first_sample_id, second_sample_id, first_site, second_site, dist, everything())
```


# Which fish are at different sites and captured far away from each other?
2019-05-20 - 4 rows of observations are flagged as "far fish".  2 rows involve 3 fish that all match to each other.  2 other rows are movements of smaller distance and are believable.  
```{r}
(far_fish <- new_pairs %>% 
  filter(dist > 50 & first_site != second_site) %>% 
   select(first_sample_id, second_sample_id, dist, contains("lig"), contains("dig"), contains("extr"), everything()) %>% 
   arrange(desc(dist)))

# investigate far fish to determine if they are true recaptures
photos <- read_csv("https://raw.githubusercontent.com/pinskylab/Clown_Fish_Tail_Color_Darrow/master/Data/fish-by-photo.csv?token=AG664YORQYQZKCBS3ZMQSGK4422VY", col_types = cols(
  image = col_character(),
  fish_table_id = col_double(),
  best_image = col_character(),
  num_images = col_double(),
  sample_id = col_character(),
  tag_id = col_double()
))

far_fish_photos <- left_join(far_fish, photos, by = c("first_sample_id" = "sample_id")) %>% 
  rename(first_image = image) %>% 
  select(-fish_table_id, -best_image, -num_images, -tag_id) %>% 
  left_join(photos, by = c("second_sample_id" = "sample_id")) %>% 
  rename(second_image = image) %>% 
  select(-fish_table_id, -best_image, -num_images, -tag_id, -contains("corr")) %>% 
  select(first_sample_id, first_image, second_sample_id, second_image, dist, first_date, second_date, first_site, second_site, everything()) %>% 
  filter(!is.na(first_image) & !is.na(second_image))





```

# Which fish are tag recaptures?
```{r}
(tag_fish <- new_pairs %>% 
  filter(first_tag_id == second_tag_id))
```



# Which fish were captured in the same year?  The fish that were captured on the same day have a note that the tail was already cut so all of these look ok.
```{r}
same_year <- new_pairs %>% 
  filter(year(first_date) == year(second_date)) %>% 
  select(first_sample_id, second_sample_id, first_date, second_date, first_fish_notes, second_fish_notes)
```
# Assign gen_ids
```{r}
max_gen_id <- gen_ids %>% 
  filter(!is.na(gen_id)) %>% 
  summarise(max = max(gen_id))
max_gen <- as.integer(max_gen_id$max[[1]])

new_gen_ids <- new_pairs %>% 
 # make the second gen_id the same as the first gen-id
   mutate(second_gen_id = ifelse(!is.na(first_gen_id), first_gen_id, second_gen_id)) %>% 
  select(contains("sample_id"), contains("gen_id"))

# is anyone still missing a gen_id
need_gen_id <- new_gen_ids %>% 
  filter(first_gen_id != second_gen_id)
# should be 0 rows

new_gen_ids <- new_gen_ids %>% 
  select(-second_gen_id) %>% 
  rename(gen_id = first_gen_id)

# combine into a list that can be imported in to the db
first <- new_gen_ids %>% 
  select(first_sample_id, gen_id) %>% 
  rename(sample_id = first_sample_id)

second <- new_gen_ids %>% 
  select(second_sample_id, gen_id) %>% 
  rename(sample_id = second_sample_id)

recap_gen_ids <- rbind(first, second) %>% 
  distinct()

# loop to make sure all recaptures of a fish get the same gen_id
for_processing <- recap_gen_ids
gens_to_keep <- tibble()
while(nrow(for_processing) > 1){
  # all samples that belong to this gen_id
  groupA <- for_processing %>% 
    filter(gen_id == for_processing$gen_id[1])
  
  # all gen_ids that belong to these samples 
  groupB <- for_processing %>% 
    filter(sample_id %in% groupA$sample_id)
  
  # all the samples that belong to these gen_ids
  groupC <- for_processing %>% 
    filter(gen_id %in% groupB$gen_id) %>% 
    group_by(gen_id) %>% 
    mutate(num_fish = n()) %>% 
    ungroup() %>% 
    mutate(max_num = max(num_fish))
  
  small_group <- groupC %>% 
    filter(num_fish != max_num) %>% 
    select(-gen_id)
  
  big_group <- groupC %>% 
    filter(num_fish == max_num)
  
  big_group <- left_join(big_group, small_group, by  = "sample_id") %>% 
    select(sample_id, gen_id)
  
  for_processing <- anti_join(for_processing, big_group, by = "sample_id")
  
  if(nrow(distinct(big_group, gen_id)) != 1){
   max_gen <- max_gen + 1
     big_group <- big_group %>% 
      mutate(gen_id = max_gen)
    
  }
  
  test <- big_group %>% 
    distinct(gen_id)
  
  stopifnot(nrow(test)==1)
  
  gens_to_keep <- rbind(gens_to_keep, big_group) %>% 
    distinct()

}

# all of the sample_ids in recap_gen_ids are  in gens to keep
test <- anti_join(recap_gen_ids, gens_to_keep, by = "sample_id")


# test 
# num_gens <- gens_to_keep %>% 
#   group_by(gen_id) %>% 
#   count()

# change the gen_ids in the fish_obs file to reflect the recaptures
fish_obs <- readRDS(here::here("data", "fish-obs.RData"))

gens_to_keep <- gens_to_keep %>% 
  rename(new_gen_id = gen_id)

fish_obs <- left_join(fish_obs, gens_to_keep, by = "sample_id")
fish_obs <- fish_obs %>% 
  mutate(gen_id = ifelse(!is.na(new_gen_id) & gen_id != new_gen_id, new_gen_id, gen_id)) %>% 
  select(-new_gen_id)

saveRDS(fish_obs, here::here("data", "fish-obs.RData"))
```


# Write new genepop with only one representative of each gen_id
```{r}
# Read in genepop
gen_file <- here("data", "seq33-03_noregeno.gen")
genedf <- read_genepop(gen_file) %>% 
  rename(ligation_id = names)

# pull sample_ids from db
sample_ids <- samp_from_lig(genedf) 

# get gen_ids for the sample_ids
gen_ids <- readRDS(here::here("data", "fish-obs.RData")) %>% 
  filter(sample_id %in% sample_ids$sample_id) %>% 
  select(sample_id, gen_id) %>% 
  left_join(sample_ids, by = "sample_id")

# replace 0000 with na
non_zero <- genedf  %>% 
  na_if(., "0000")

# count how many loci are represented on each line
numloci <- non_zero %>% 
  is.na %>% 
  `!` %>% 
  rowSums

# add numloci as a column
numgen <- cbind(gen_ids, numloci)

# create a data frame of sample ids to keep or drop based on the number of loci present
keep_drop <- numgen %>% 
  # select only the columns to identify which to keep
  select(gen_id, ligation_id, numloci) %>%
  group_by(gen_id) %>% 
  # create a maxloci column that holds the most loci each sample id carries
  mutate(maxloci = max(numloci), 
         # create a drop column that holds the decision to keep or drop that row
         drop = ifelse(numloci == maxloci, "KEEP", "DROP")) %>% 
  # keep only the columns that hold the maxloci and say "KEEP"
  filter(drop == "KEEP") %>% 
  ungroup() %>% 
  # keep only the columns needed to identify these "keeper rows"
  select(ligation_id)

# keep only the version of the sample id that has the most loci
no_recap <- numgen %>% 
  filter(ligation_id %in% keep_drop$ligation_id)


# Some samples were not dropped because both regenotypes have the same number of loci. This is just one line out of multiple, so keeping just the one line 
recaps <- no_recap %>%
  filter(duplicated(no_recap$gen_id)) %>%
  select(gen_id, ligation_id)

# drop the ligation_ids for these duplicated samples
no_recap1 <- no_recap %>% 
  filter(!ligation_id %in% recaps$ligation_id)

# rerun the above line to make sure no recaps remain

# filter the genedf according to this list
norecaps <- genedf %>% 
  filter(ligation_id %in% no_recap1$ligation_id)

```
# Write the genepop
```{r}
# Build the genepop components
msg <- c("This genepop file was generated using a script called process_genepop.Rmd written by Michelle Stuart ")
write_lines(msg, path = str_c(here("data", "seq33-03_norecap.gen"), sep = ""), append = F)

# find all of the column names that contain contig and collapse them into a comma separated string
loci <-  str_c(names(select(norecaps, contains("contig"))), collapse = ",")
write_lines(loci, path = str_c(here("data", "seq33-03_norecap.gen"), sep = ""), append = T)

pop <- "pop"
write_lines(pop, path = str_c(here("data", "seq33-03_norecap.gen"), sep = ""), append = T)

gene <- vector()
sample <- vector()
for (i in 1:nrow(norecaps)){
  gene[i] <- str_c(select(norecaps[i,], contains("contig")), collapse = " ")
  sample[i] <- str_c(norecaps$ligation_id[i], gene[i], sep = ", ")
  write_lines(sample[i], path = str_c(here("data", "seq33-03_norecap.gen"), sep = ""), append = T)
}
```

# Then run the recaptured-fish.Rmd protocol to make sure the gen_ids and tag_ids are all matched up in fish-obs.Rdata.