---
title: "Double checking fish lacking genid"
output: html_notebook
---

Katrina found fish in her analysis are in the sequencing data and have a sample_id but no gen_id.

Double checking to make sure they weren't missed in the gen_id assignment.

Note, to have a gen_id, the sample should have been sucessfully sequenced and passed filtering.

```{r setup, include=FALSE}
pacman::p_load(tidyverse, here, clownfish, install=FALSE)
# library(tidylog)
source(here("scripts", "gen_helpers.R"))
source("~/Documents/clownfish-pkg/R/db_connections.R")
leyte <- read_db("Leyte")
lab <- read_db("Laboratory")

nogenid <- readRDS(here("data", "172_nogenid.rds"))
```

Get all of the labwork for the fish in the nogenid table
```{r labwork}
labwork <- get_extr() %>% 
  filter(sample_id %in% nogenid$sample_id) %>% 
  select(sample_id, extraction_id) %>% 
  left_join(get_dig(), by = "extraction_id") %>% 
  select(sample_id, extraction_id, digest_id) %>% 
  left_join(get_lig(), by = "digest_id") %>% 
  select(sample_id, extraction_id, digest_id, ligation_id, retained)

meta_data <- get_fish() %>% 
  filter(sample_id %in% labwork$sample_id)

full_info <- left_join(labwork, select(meta_data, sample_id, gen_id), by = "sample_id")

knitr::kable(full_info) %>% 
  kableExtra::kable_styling()

```

Pull in the genepop to see if these samples passed sequencing and filtering
```{r}
genfile <- here("data", "seq03-33_identity", "seq33_03_baits_only_SNPs.gen")
genedf <- read_genepop(genfile) %>% 
  select(names) %>% 
  rename(ligation_id = names) %>% 
  mutate(ligation_id = str_replace(ligation_id, "APCL_", ""), 
         ligation_id = str_replace(ligation_id, ".F", ""))

# which regenotypes are present in the genepop
regenos <- genedf %>% 
  filter(nchar(ligation_id) > 5)

# what about post identity analysis genepop
id_genfile <- here("data", "seq03-33_norecap.gen")
id_genedf <- read_genepop(id_genfile) %>% 
  select(names) %>% 
  rename(ligation_id = names) 

# which samples are in the genedf?
need_gen_id <- full_info %>% 
  filter(ligation_id %in% genedf$ligation_id)

knitr::kable(need_gen_id) %>% 
  kableExtra::kable_styling()

saveRDS(need_gen_id, here("data", "need_gen_id.RData"))
```

Copied the need_gen_id.RData file over to the leyteBuildDB/data folder to be added to the database.