---
title: "Color transitions in Leyte clownfish"
output: html_notebook
---
Compare time, size and color transitions.

```{r setup, include=FALSE}
pacman::p_load(tidyverse, here, clownfish, install=FALSE)
# library(tidylog)

# because the myconfig db connection is still not working
source("~/Documents/clownfish-pkg/R/db_connections.R")
leyte <- read_db("Leyte")
```


```{r fish size}
# pull in size and color data for the fish in the fish_recaps table
add_colors <- fish_anem_dive() %>% 
  filter(fish_table_id %in% fish_recaps$fish_table_id) %>% 
  select(fish_table_id, size, color, sex)

# add size & color to fish_recaps
fish_colors <- left_join(fish_recaps, add_colors, by = "fish_table_id") %>% 
  filter(!is.na(color))

# which fish change colors
diff_colors <- fish_colors %>% 
  select(recap_id, color) %>% 
  distinct() %>% 
  group_by(recap_id) %>%
  count() %>% 
  filter(n > 1)

# create a table of recaptured fish with multiple color observations
fish_diff <- fish_colors %>% 
  filter(recap_id %in% diff_colors$recap_id) %>% 
  arrange(recap_id, date) %>% 
  select(fish_table_id, recap_id, date, size, color, sex) %>% 
  distinct() %>% 
# assign sex as a factor
  mutate(sex = ordered(as.factor(sex), levels = c("J", "M", "F")))

# create a placeholder for fish that need to be checked
out_of_order <- c()

for (i in diff_colors$recap_id){
  x <- fish_diff %>% 
    filter(recap_id == i) %>% 
    arrange(date)
  
  if(is.unsorted(x$sex)){
    out_of_order <- c(out_of_order, x$recap_id)
  }
  }

check_these_fish <- fish_diff %>% 
  filter(recap_id %in% out_of_order) %>% 
  distinct() %>% 
  arrange(recap_id, date)


```
Visually check for fish that don't follow the normal progression and update the change database document as needed.  

I noticed that some fish were 7 and "Y" with a "J" sex assignment and the next year were 8.3 with "YP" and a "F" sex assignment.  I was going to question these, but then saw some fish that were 4.3 "Y" and the next year were 9.3 "YP", so I am allowing that fish can rapidly be promoted in the social strucutre if the situation allows it.
